
---
title: "Characterizing Salmon Shed Tank Temperature, Conductivity, and Water Chemistry"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Salmon Shed Tanks
Date: 2018-2019 (R document January-February 2021)




# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(here)
library(stringr)
library(data.table)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
library(arsenal)
library(compareDF)
library(metacsv)
#for graphing
library(ggplot2)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```



# 1.) Setting Working Directory
```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
# setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks")


```


# 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 2.) Creating the initial Dataframes
#*********************************


#set working directory to the correct folder
# setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks")
# here()

# former "dtank"

library(here)
here()

dOrion <- read_csv(here("01_rawData","SpecData_2021.02.11_masterfile_salmonshed_chumhouse.csv"))

#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*

# write_meta_template(dOrion, here("01_rawData",
#                                  "masterfile_salmonshed_chumhouse.csv"),
#                             embedded = TRUE)
# 
# meta_dOrion <- read_meta(here("01_rawData",
#                              "masterfile_salmonshed_chumhouse_withMeta.csv"))
# 
# #Just the data
# meta_dOrion2 <- read_meta(here("01_rawData",
#                              "masterfile_salmonshed_chumhouse_withMeta.csv"))$data


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - -  - - - - - - - - - - - - |

# former "dUDAsalmon" and/or dfSalinity
dFishCareUDA <- read_csv(here("01_rawData", "2021.02.18_FishCareLog_salinity.csv")) 
dim(dFishCareUDA)

#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*
# meta_dFishCareUDA <- read_meta(here("01_rawData", "2021.02.18_FishCareLog_salinity.csv"))
# 
# write_meta_template(meta_dFishCareUDA, "META_2021.02.18_FishCareLog_salinity.csv",
#                     embedded = TRUE)



#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# former UDAconductivity
# Raw file from UDA
# dShedUDA <- read.csv(file = "2019 SS UDA Log.csv", stringsAsFactors = FALSE)
# dim(dShedUDA)
# Transformed File
dShedUDA <- read_csv(here("01_rawData", "2021.02.18_pH_UDA.csv"))
dim(dShedUDA)
#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*
# meta_dShedUDA <- read_meta(here("01_rawData", "2021.02.18_pH_UDA.csv"))
# 
# write_meta_template(meta_dShedUDA, "META_2021.02.18_pH_UDA.csv",
#                     embedded = TRUE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dHOBOppt <- read_csv(here("01_rawData","2021.02.18b_dHOBOlogCNDCT.csv"))
dim(dHOBOppt)
#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*
# meta_dHOBOppt<- read_meta(here("01_rawData", "2021.02.18b_dHOBOlogCNDCT.csv"))
# 
# write_meta_template(meta_dHOBOppt, "META_2021.02.18b_dHOBOlogCNDCT.csv.csv",
#                     embedded = TRUE)


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dShedSalinity <- read_csv(here("01_rawData", "2019 SS UDA Log.csv"))

#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*
# meta_dShedSalinity<- read_meta(here("01_rawData", "2019 SS UDA Log.csv.csv"))
# 
# write_meta_template(meta_dShedSalinity, "META_2019 SS UDA Log.csv.csv.csv",
#                     embedded = TRUE)



```
Dataframes mentioned throughout the document
dOrion = all SPEC files 
dFishCareUDA = information from Chase's fish care log 
dShedUDA = UDA information from the Salmon Shed recorded by OA lab personnel  
dHOBOppt = Includes salinity readings from the conductivity logger


# 3.) Creating dateTime objects 
```{r 3.) Creating dateTime objects, echo=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 3.) Creating dateTime objects  
#*********************************
dOrion$ObservationDate <- ""
dOrion$ObservationDate <- as.POSIXct(dOrion$date, tz = "UTC", "%m/%d/%y")

dFishCareUDA$ObservationDate <- ""
dFishCareUDA$ObservationDate <- as.POSIXct(dFishCareUDA$Date, tz = "UTC", "%m/%d/%y")

dShedUDA$ObservationDate <- ""
dShedUDA$ObservationDate <- as.POSIXct(dShedUDA$date, tz = "UTC", "%m/%d/%y")

dHOBOppt$ObservationDate <- ""
dHOBOppt$ObservationDate <- as.POSIXct(dHOBOppt$dateTime, tz = "UTC", "%m/%d/%y %H:%M")

dShedSalinity$ObservationDate <- ""
dShedSalinity$ObservationDate <- as.POSIXct(dShedSalinity$Date, tz = "UTC", "%m/%d/%y")

```
First Observation recorded as of August 10th 2018


# 4.) Creating Treatments
```{r 4.) Creating Treatments}
#*********************************
## 4.) Creating Treatments 
#********************************
# 6 tanks
# 3 replicates of the high CO2 conditions
# 3 replicates of ambient conditions

# Review of 4 important datasets
names(dOrion)
names(dFishCareUDA)
names(dShedUDA)
names(dHOBOppt)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dOrion$unit_number <- as.character(dOrion$unit_number)
dOrion$treatment <- ""
dOrion$treatment[dOrion$unit_number == "2" | dOrion$unit_number== "4" | dOrion$unit_number== "6"] <- "highCO2_juvenileDGN"
dOrion$treatment[dOrion$unit_number == "1" | dOrion$unit_number== "3" | dOrion$unit_number== "5"] <- "ambient_juvenileDGN"
dOrion$treatment[dOrion$unit_number == "7"] <- "ambient"
dOrion$treatment[dOrion$unit_number == "8"] <- "ambient_chumhouse"

dOrion$location <- ""
dOrion$location[dOrion$treatment == "highCO2_juvenileDGN" | dOrion$treatment == "ambient_juvenileDGN" | dOrion$treatment == "ambient"] <- "salmonShed"

dOrion$location[dOrion$unit_number == "8"] <- "ambient_chumhouse"

dOrion$sensortype <- ""
dOrion$sensortype <- "OrionStarA112"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#Treatment is being created for the Salinity Timeseries 
## - however no water chemistry data was collected
# all values are treated as chumhouse or salmon shed ambient
dFishCareUDA$treatment[dFishCareUDA$location == "salmonShed" ] <- "ambient"
dFishCareUDA$treatment[dFishCareUDA$location == "chumHouse" ] <- "ambient_chumhouse"

dFishCareUDA$sensortype <- ""
dFishCareUDA$sensortype[dFishCareUDA$location == "salmonShed" ] <- "wallUDA_salmonShed"
dFishCareUDA$sensortype[dFishCareUDA$location == "chumHouse" ] <- "wallUDA_chumhouse"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# dShedUDA file uses same unit_number identifers as SPEC file
dShedUDA$unit_number <- as.character(dShedUDA$unit_number)
dShedUDA$treatment <- ""
dShedUDA$treatment[dShedUDA$unit_number == "2" | dShedUDA$unit_number== "4" | dShedUDA$unit_number== "6"] <- "highCO2_juvenileDGN"
dShedUDA$treatment[dShedUDA$unit_number == "1" | dShedUDA$unit_number== "3" | dShedUDA$unit_number== "5"] <- "ambient_juvenileDGN"

dShedUDA$sensortype <- ""
dShedUDA$sensortype <- "wallUDA_salmonShed"

dShedUDA$location <- ""
dShedUDA$location <- "salmonShed"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dHOBOppt$treatment <- ""
dHOBOppt$treatment <- "ambient"


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dShedSalinity$treatment<- ""
dShedSalinity$treatment<- "ambient"
dShedSalinity$location <- ""
dShedSalinity$location <- "salmonShed"
dShedSalinity$sensortype <- ""
dShedSalinity$sensortype <- "wallUDA_salmonShed"

```



# 5.) Salinity and Waterchemistry Dataframes

```{r}

names(dOrion)

dOrion_Salinity <- select(dOrion,
                          salinity,
                          ObservationDate,
                          treatment,
                          location,
                          sensortype)



dOrion_pH <- select(dOrion,
                          pH,
                          ObservationDate,
                          treatment,
                          location,
                          sensortype)

names(dFishCareUDA) 

dFishCareUDA_Salinity <- select(dFishCareUDA,
                          salinity,
                          ObservationDate,
                          treatment,
                          location,
                          sensortype)


dFishCareUDA_temp <- select(dFishCareUDA,
                          temp,
                          ObservationDate,
                          location,
                          sensortype)



names(dShedUDA)

dShedUDA_pH <- select(dShedUDA,
                          pH,
                          ObservationDate,
                          treatment,
                          location,
                          sensortype)

dShedUDA_temp <- select(dShedUDA,
                          temp,
                          ObservationDate,
                          location,
                          sensortype)


names(dHOBOppt)


dHOBOppt_Salinity <- select(dHOBOppt,
                          salinity,
                          ObservationDate,
                          treatment,
                          location,
                          sensortype)

dSalmonShed_Salinity <- select(dShedSalinity,
                          salinity,
                          ObservationDate,
                          treatment,
                          location,
                          sensortype)


#*********************************
## 5.1) Creating a Master Dataframe - Salinity, pH, & temp
#********************************

Master_Salinity <- merge(merge(merge(
  dOrion_Salinity,
  dFishCareUDA_Salinity, all = TRUE),
  dHOBOppt_Salinity, all = TRUE),
  dSalmonShed_Salinity, all = TRUE)
Master_Salinity$salinity <- as.numeric(Master_Salinity$salinity)

write.csv(Master_Salinity, "2021.03.04_Master_Salinity_log.csv")

Master_pH <- merge(dOrion_pH, dShedUDA_pH, all = TRUE)
Master_pH$pH <- as.numeric(Master_pH$pH )

write.csv(Master_pH, "2021.03.04_Master_pH_log.csv")

Master_temp <- merge(dFishCareUDA_temp, dShedUDA_temp, all = TRUE)
Master_temp$temp <- as.numeric(Master_temp$temp)
write.csv(Master_temp, "2021.03.04_Master_temp_log.csv")


```


#### 5.1a) dOrion Dataframes - Exploring the Salinity history (1 dataframe at a time)
```{r dOrion Dataframe Salinty Plot}

# dOrion_Salinity <- group_by(dOrion_Salinity$ObservationDate)

 ggplot(dOrion_Salinity, aes(ObservationDate, salinity)) +
  geom_point() +
  ylim(24,33) +
  ggtitle("Salinity Values from Orion Star A112 Salinity Probe")

# 
#  ggplot(dOrion, aes(date, salinity)) + 
#   geom_point() +
#   ylim(24,33) +
#   ggtitle("Salinity Values from Orion Star A112 Salinity Probe")


```



#### 5.1a) dFishcareUDA Dataframes - Exploring the Salinity history (1 dataframe at a time)
```{r dFishcareUDA  Dataframe Salinty Plot}

# dOrion_Salinity <- group_by(dOrion_Salinity$ObservationDate)

 ggplot(dFishCareUDA_Salinity, aes(ObservationDate, salinity)) +
  geom_point() +
  # ylim(24,33) +
  ggtitle("Salinity Values from Wall Mounted UDA Chumhouse & Salmon Shed")


 # ggplot(dFishCareUDA, aes(Date, salinity)) + 
 #  geom_point() +
 #  # ylim(24,33) +
 #  ggtitle("Salinity Values from Wall Mounted UDA Chumhouse & Salmon Shed")


```

#### 5.1b) dShedSalinity Dataframe - Exploring the Salinity history (1 dataframe at a time)
```{r dSalmonShed_Salinity  Dataframe Salinty Plot}


 ggplot(dSalmonShed_Salinity, aes(ObservationDate, salinity)) +
  geom_point() +
  # ylim(24,33) +
  ggtitle("Salinity Values from Wall Mounted (just) Salmon Shed")


 # ggplot(dFishCareUDA, aes(Date, salinity)) + 
 #  geom_point() +
 #  # ylim(24,33) +
 #  ggtitle("Salinity Values from Wall Mounted UDA Chumhouse & Salmon Shed")


```




#### 5.2) Salinity Dataframes - Exploring the HOBOlogger history
```{r}

# dHOBOsalinity <- group_by(dHOBOsalinity$dateTime)

ggplot(dHOBOppt, aes(ObservationDate, salinity)) + 
  geom_point() +
  ylim(24,30) +
  ggtitle("Salinity Values from HOBOlogger Salinity Probe") 



```


#### 5.1) Salinity Dataframes - Exploring the HOBOlogger history
```{r}

# dHOBOsalinity <- group_by(dHOBOsalinity$dateTime)

HOBOProbe_Temp_plot <- ggplot(dHOBOppt, aes(ObservationDate, temperature)) + 
  geom_point() +
  # ylim(24,30) +
  ggtitle("Temperature Values from HOBOlogger Salinity Probe") 

HOBOProbe_Temp_plot


```





#### 5.3) dOrion Dataframes - Exploring the pH history (1 dataframe at a time)
```{r dOrion Dataframe pH Plot}


 ggplot(dOrion_pH, aes(ObservationDate, pH)) +
   geom_point(aes(colour=treatment)) + 
  ggtitle("pH Values from SPEC masterfile")

# 
#  ggplot(dOrion, aes(date, salinity)) + 
#   geom_point() +
#   ylim(24,33) +
#   ggtitle("Salinity Values from Orion Star A112 Salinity Probe")


```





#### 5.4) Master Dataframes - Exploring the Salinity history 
```{r Master Salinity Dataframe ppt Plot}

Master_Salinity$salinity <- as.numeric(Master_Salinity$salinity)

 ggplot(Master_Salinity, aes(ObservationDate, salinity)) +
  geom_point(aes(colour=sensortype, point=)) +
  # facet_wrap(location) +
  ylim(24,33) +
  ggtitle("all Salinity Values from all Probes, all locations") 


```




#### 5.5) Master Dataframes - Exploring the pH history 
```{r Master pH Dataframe  Plot}


 ggplot(Master_pH, aes(ObservationDate, pH)) +
  geom_point(aes(colour=treatment, point=)) +
  # facet_wrap(location) +
  # ylim(24,33) +
  ggtitle("all pH Values from all Probes, all locations") 


```



#### 5.5) Master Dataframes - Exploring the pH history 
```{r Master pH Dataframe  Plot}


 ggplot(Master_pH, aes(ObservationDate, pH)) +
  geom_point(aes(colour=treatment, point=)) +
  # facet_wrap(location) +
  ylim(6,8.5) +
  ggtitle("all pH Values from all Probes, all locations") 


```

#### 5.6) Master Dataframes - Exploring the pH history 
```{r Master pH Dataframe Sensor Plot}


 ggplot(Master_pH, aes(ObservationDate, pH)) +
  geom_point(aes(colour=sensortype, point=)) +
  # facet_wrap(location) +
  ylim(6,8.5) +
  ggtitle("all pH Values from all Probes, colored by sensor type") 


```


#### 5.6) Master Dataframes - Exploring the pH history 
```{r Master pH Dataframe Sensor Plot}


Master_temp$temp <- as.numeric(Master_temp$temp)

 ggplot(Master_temp, aes(ObservationDate, temp)) +
  geom_point(aes(colour=location, point=)) +
  # facet_wrap(location) +
  # ylim(6,8.5) +
  ggtitle("all Temperature Values from all Probes, colored by sensor type") 


```


# 6.) Water Chemistry - Cleaning and Transposing UDA Data
#### 6.1) pH plots per tank timeseries
```{r 6.1) pH plots per tank timeseries, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 6.1) pH plots -Timeseries Plots - Bringing Together UDA plots for the different tanks
#*********************************

UDAtank01 <- read.csv(here("02_processedData", "Tank01UDALog.csv"))
UDAtank02 <- read.csv(here("02_processedData", "Tank02UDALog.csv"))
UDAtank04 <- read.csv(here("02_processedData", "Tank04UDALog.csv"))
UDAtank05 <- read.csv(here("02_processedData", "Tank05UDALog.csv"))
UDAtank06 <- read.csv(here("02_processedData", "Tank06UDALog.csv"))

pHdtankUDA <- rbind(UDAtank06,
                    UDAtank05,  
                    UDAtank04,
                    UDAtank02,
                    UDAtank01)

#|- -- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
```



# Executive Summary


UDA sensors for ambient tank 01 appears to experience significant drift April and beyond.

SPEC data confirms the High CO2 treatment target pH. 


```{r}
# pHtanklog.summary <- pHtanklog %>% group_by(treatment, sensortype) %>%
#   dplyr::summarize(sd = sd(pH, na.rm = TRUE), 
#             mean = mean(pH, na.rm = TRUE), 
#             median = median(pH, na.rm = TRUE),
#             IQR = IQR(pH, na.rm = TRUE),
#             n = n()) %>%
#   mutate(se = sd/sqrt(n)) %>%
#   mutate(ci = se*1.96)
# 
# write.csv(pHtanklog.summary, "2021.02.02_pHtanklog.summary.csv")
# kable(pHtanklog.summary, digits = 4)


```





```{r}
# pHboxplots1 <- ggplot(pHtanklog, aes(treatment, pH)) +
#             geom_jitter(color = "grey") +
#             geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
#             geom_point(data = pHtanklog.summary, aes(x=treatment, y=mean), size=5, color = "purple") + 
#             geom_errorbar(data = pHtanklog.summary, 
#                           aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
#                           color = "blue") +
#             geom_errorbar(data = pHtanklog.summary,
#                           aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
#                           colour = "red") +
#             # facet_wrap(~TrialID) +
#             ggtitle("Salmon Shed pH grouped by Treatment") +
#             theme_bw() 
# 
# pHboxplots1

```

```{r}
# pHboxplots2 <- ggplot(pHtanklog, aes(sensortype, pH)) +
#             geom_jitter(color = "grey") +
#             geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
#             geom_point(data = pHtanklog.summary, aes(x=treatment, y=mean), size=5, color = "purple") +
#             geom_errorbar(data = pHtanklog.summary, 
#                           aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
#                           color = "blue") +
#             geom_errorbar(data = pHtanklog.summary,
#                           aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
#                           colour = "red") +
#             # facet_wrap(~TrialID) +
#             ggtitle("Salmon Shed pH grouped by Sensor") +
#             theme_bw() 
# 
# pHboxplots2
```



```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT

