
---
title: "Characterizing Salmon Shed Tank Temperature, Conductivity, and Water Chemistry"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Salmon Shed Tanks
Date: 2018-2019 (R document January-February 2021)


2021.02.11 
[_] graph for salinity for orion against wall mounted conductivty probe
[_] graph temperature for chum house against salmon shed
[_] need to get model number for that wall mounted conductivty display and related probe
[_] include HOBOlogger conductivity material


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(here)
library(stringr)
library(data.table)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
library(arsenal)
library(compareDF)
#for graphing
library(ggplot2)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```



# 1.) Setting Working Directory
```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
# setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks")


```


# 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 2.) Creating the initial Dataframe, dtank
#*********************************


#set working directory to the correct folder
# setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks")
here()

# former "dtank"

library(here)
## Example
# d <- read_csv(here("output", "crab_combine_wide_stage.csv"))

dOrion <- read_csv(here("01_rawData","SpecData_2021.02.11_masterfile_salmonshed_chumhouse.csv"))


  file = "SpecData_2021.02.11_masterfile_salmonshed_chumhouse.csv", 
                  stringsAsFactors = FALSE)
dOrion <- read.csv(file = "SpecData_2021.02.11_masterfile_salmonshed_chumhouse.csv", 
                  stringsAsFactors = FALSE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - -  - - - - - - - - - - - - |

# former "dUDAsalmon" and/or dfSalinity
dSalmonPPT <- read.csv(file = "2021.02.18_FishCareLog_salinity.csv", 
                  stringsAsFactors = FALSE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# former UDAconductivity
# Raw file from UDA
# dShedUDA <- read.csv(file = "2019 SS UDA Log.csv", stringsAsFactors = FALSE)
# dim(dShedUDA)
# Transformed File
dShedUDA <- read.csv(file = "2021.02.18_pH_Salinity_UDA.csv", stringsAsFactors = FALSE)
dim(dShedUDA)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dHOBOsalinity <- read.csv(file = "2021.02.18b_dHOBOlogCNDCT.csv", stringsAsFactors = FALSE)
dim(dHOBOsalinity)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```
Dataframes mentioned throughout the document
dOrion = all SPEC files 
dSalmonPPT = information from Chase's fish care log 
dShedUDA = UDA information from the Salmon Shed recorded by OA lab personnel  
dHOBOsalinity= Includes salinity readings from the conductivity logger



# 3.) Creating dateTime objects 
```{r 3.) Creating dateTime objects, echo=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 3.) Creating dateTime objects  
#*********************************
dOrion$ObservationDate <- ""
dOrion$ObservationDate <- as.POSIXct(dOrion$date, tz = "UTC", "%Y-%m-%d")

dSalmonPPT$ObservationDate <- ""
dSalmonPPT$ObservationDate <- as.POSIXct(dSalmonPPT$Date, tz = "UTC", "%m/%d/%y")

dShedUDA$ObservationDate <- ""
dShedUDA$ObservationDate <- as.POSIXct(dShedUDA$date, tz = "UTC", "%m/%d/%y")

dHOBOsalinity$ObservationDate <- ""
dHOBOsalinity$ObservationDate <- as.POSIXct(dHOBOsalinity$dateTime, tz = "UTC", "%m/%d/%y %H:%M")



```
First Observation recorded as of August 10th 2018


# 4.) Creating Treatments
```{r 4.) Creating Treatments, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 4.) Creating Treatments 
#********************************
# 6 tanks
# 3 replicates of the high CO2 conditions
# 3 replicates of ambient conditions

# Review of 4 important datasets
names(dOrion)
names(dSalmonPPT)
names(dShedUDA)
names(dHOBOsalinity)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dOrion$unit_number <- as.character(dOrion$unit_number)
dOrion$treatment <- ""
dOrion$treatment[dOrion$unit_number == "2" | dOrion$unit_number== "4" | dOrion$unit_number== "6"] <- "highCO2_juvenileDGN"
dOrion$treatment[dOrion$unit_number == "1" | dOrion$unit_number== "3" | dOrion$unit_number== "5"] <- "ambient_juvenileDGN"
dOrion$treatment[dOrion$unit_number == "7"] <- "ambient"
dOrion$treatment[dOrion$unit_number == "8"] <- "ambient_chumhouse"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#Treatment is being created for the Salinity Timeseries 
## - however no water chemistry data was collected
# all values are treated as chumhouse or salmon shed ambient
dSalmonPPT$location[dSalmonPPT$location == "salmonShed" ] <- "ambient"
dSalmonPPT$location[dSalmonPPT$location == "chumHouse" ] <- "ambient_chumhouse"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# dShedUDA file uses same unit_number identifers as SPEC file
dShedUDA$unit_number <- as.character(dShedUDA$unit_number)
dShedUDA$treatment <- ""
dShedUDA$treatment[dShedUDA$unit_number == "2" | dShedUDA$unit_number== "4" | dShedUDA$unit_number== "6"] <- "highCO2_juvenileDGN"
dShedUDA$treatment[dShedUDA$unit_number == "1" | dShedUDA$unit_number== "3" | dShedUDA$unit_number== "5"] <- "ambient_juvenileDGN"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dHOBOsalinity$treatment <- ""
dHOBOsalinity$treatment <- "ambient"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```



# 5.) Salinity Dataframes

```{r}

names(dOrion)
names(dSalmonPPT)
names(dShedUDA)
names(dHOBOsalinity)

# dOrion <- dOrion %>% rename(salinity = salinity) 
# dSalmonPPT$salinity <- ""
# dSalmonPPT$salinity <- dSalmonPPT$Salinity
# 
# dSalmonPPT <- subset( dSalmonPPT, select = -c(Salinity))

dSalmonPPT$salinity <- rename(dSalmonPPT, Salinity = salinity)
dSalmonPPT <- dSalmonPPT %>% rename(Salinity = salinity) 
# dShedUDA <- dShedUDA %>% rename(Salinity = salinity) 

# dHOBOsalinity <- dHOBOsalinity %>% rename(salinityPPT = salinity) 


```



#### 5.0) Salinity Dataframes - Exploring the HOBOlogger history
```{r}

# dHOBOsalinity <- group_by(dHOBOsalinity$dateTime)

HOBOSalinityProbe_plot <- ggplot(dHOBOsalinity, aes(ObservationDate, salinityPPT)) + 
  geom_point() +
  ylim(24,30) +
  ggtitle("Salinity Values from HOBOlogger Salinity Probe") 

HOBOSalinityProbe_plot




```





#### 5.1) Salinity Plots
```{r 5.1) Salinity Plots, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.1) Timeseries Plot
#*********************************
# dtank$salinity <- as.numeric(dtank$salinity)

dOrion$salinity <- as.numeric(dOrion$salinity)

SalinityProbe_SalmonShed_plot <- ggplot(dOrion, aes(ObservationDate, salinity)) + 
  geom_point(aes(colour=treatment, point=)) + 
  ggtitle("Salinity Values from Handheld Orion Salinity Probe") 

SalinityProbe_SalmonShed_plot 

```


#### 5.1a) Merging salinity data for plots
```{r 5.1a) Merging salinity data for plots, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.1a) Salinity Data for Timeseries Plot
#*********************************

variable.names(dOrion)
variable.names(dSalmonPPT)
variable.names(dShedUDA)
variable.names(dHOBOSalinity)



dOrion_log <- subset( dOrion, select = -c(id_1,
                                         T4.pH,
                                         T4.temp,         
                                         T3.pH,
                                         T3.temp,
                                         T5.pH,
                                         T5.temp,
                                         T6.pH,
                                         T6.temp,
                                         T2.pH,           
                                         T2.temp,         
                                         T1.pH,          
                                         T1.temp))
colnames(UDACNDCT)[1] <- "salinity"
UDACNDCT$sensortype <- ""
# Toroidal Conductivity Monitor Model Q46CT
UDACNDCT$sensortype <- "EXO_Wallprobe"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


dOrion_log <- subset( dOrion_log, select = -c(unit,
                                         unit_number,
                                         pHinsitu,
                                         dateString,
                                         experiment, 
                                         id_1, 
                                         id_2, 
                                         id_3, 
                                         time, 
                                         date, 
                                         pHat25, 
                                         fileName, 
                                         unit_ID, 
                                         alk, 
                                         treatment,
                                         insituTemp))
SPECCNDCT$sensortype <- ""
# ThermoScientific Orion Star A322
SPECCNDCT$sensortype <- "Orion"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dTankCNDCT <- merge(UDACNDCT, SPECCNDCT, all = TRUE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```
Determine if salinity units are both PSU


```{r, 5.2 Salinity Values}

names(dfSalinity)
# [1] "Date"              "Species"           "Tank"              "Water.Temperature"
# [5] "salinity"          "location"          "sensortype"        "ObservationDate"  

dfSalinity$Salinity <- as.numeric(dfSalinity$Salinity)
na.omit(dfSalinity, cols=salinity)

chronoSalinity1 <- subset(dfSalinity, select = -c(Species, 
                                         Tank,
                                         Water.Temperature))

# extract water temperature from the ChumHouse

chumHouse_Temp <- subset(dfSalinity, select = c(Date, 
                                         Tank,
                                         Water.Temperature))


# chronoSalinity1 <- chronoSalinity1  %>% filter(location %in% c("salmonShed"))
# chronoSalinity1 <- subset( chronoSalinity1, select = -c(location))
#104 of 200 observations remaining if removing another other location


chronoSalinity1$Salinity 

names(chronoSalinity1)[names(chronoSalinity1) == "Salinity"] <- "salinity"


dTankCNDCT
names(dTankCNDCT)
# [1] "salinity"        "ObservationDate" "sensortype"      "treatName"       "treatpH"        
# [6] "treatTemp"       "treatOther"      "dic"             "tankTemp"  

chronoSalinity2 <- dTankCNDCT

chronoSalinity2 <- subset(chronoSalinity2, select = -c(sensortype, 
                                         treatName,
                                         treatpH,
                                         treatTemp,
                                         treatOther,
                                         dic,
                                         tankTemp))

chronoSalinity2$sensortype <- ""
chronoSalinity2$sensortype <- "Exo_WallDisplay"

chronoSalinity2$location <- ""
chronoSalinity2$location <- "salmonShed"

# # Subset for the Chum House with Tank 8
# chronoSalinity2 <- chronoSalinity2 %>% mutate(location=case_when(
#                           (chronoSalinity2$unit_number == "8") ~"chumHouse"))
#                        

chronoSalinity <- merge(chronoSalinity1, chronoSalinity2, all = TRUE)


```



# Probe Types
```{r}
dOrion$sensortypeSalinity
dSalmonPPT$ 
dHOBOsalinity$

# Toroidal Conductivity Monitor Model Q46CT
UDACNDCT$sensortype <- "EXO_Wallprobe"


SPECCNDCT$sensortype <- ""
# ThermoScientific Orion Star A322
SPECCNDCT$sensortype <- "Orion"
```





```{r}
ggplot(chronoSalinity, aes(ObservationDate, salinity)) + 
  geom_point(aes(colour=location, point=)) + 
  ggtitle("Salinity Values from All UDA observations in Salmon Shed") 
```



#### 5.1b) Different Salinity Probes' Data
```{r 5.1b) Different Salinity Probes Data, echo=FALSE, message=FALSE, warning=FALSE}


dTankCNDCT <- merge(UDACNDCT, SPECCNDCT, all = TRUE)
dTankCNDCT$location <- ""
dTankCNDCT$location <- "salmonShed"

# # Subset for the Chum House with Tank 8
# dTankCNDCT<- dTankCNDCT %>% mutate(location=case_when(
#                           (dTankCNDCT$unit_number == "8") ~"chumHouse"))

dTANKConductivity <- merge(dTankCNDCT, chronoSalinity, all = TRUE)

PSUplot <- ggplot(dTANKConductivity, aes(x=ObservationDate, y=salinity)) + 
  geom_point(aes(colour=sensortype, point=)) + 
  ggtitle("Salmon Shed Salinity Values") 
PSUplot

```

```{r}

PSUplot <- ggplot(dTANKConductivity, aes(x=ObservationDate, y=salinity)) + 
  geom_point(aes(colour=location, point=)) + 
  ggtitle("Salinity Values by Location") 
PSUplot

```


Temperature
```{r}
ufos <- ufos %>% rename(spotter.comments = comments) 

```



# 6.) Water Chemistry
#### 6.1) pH plots per tank timeseries
```{r 6.1) pH plots per tank timeseries, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 6.1) pH plots -Timeseries Plots - Bringing Together UDA plots for the different tanks
#*********************************

UDAtank01 <- read.csv(file = "Tank01UDALog.csv", stringsAsFactors = FALSE)
UDAtank02 <- read.csv(file = "Tank02UDALog.csv", stringsAsFactors = FALSE)
UDAtank04 <- read.csv(file = "Tank04UDALog.csv", stringsAsFactors = FALSE)
UDAtank05 <- read.csv(file = "Tank05UDALog.csv", stringsAsFactors = FALSE)
UDAtank06 <- read.csv(file = "Tank06UDALog.csv", stringsAsFactors = FALSE)

pHdtankUDA <- rbind(UDAtank06,
                    UDAtank05,  
                    UDAtank04,
                    UDAtank02,
                    UDAtank01)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


```



#### 6.1a) pH plots -Timeseries Plots - UDA
```{r 6.1a) pH plots -Timeseries Plots - UDA, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 6.1a) pH plots -Timeseries Plots - UDA sensor type, update dates
#*********************************

variable.names(pHdtankUDA)
# > variable.names(pHdtankUDA)
# [1] "experiment"  "unit"        "unit_number" "date"        "pH"          "temp" 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


# not sure if this is the correct UDA sensor model number 
# UDA2182UniversalDualAnalyzer
pHdtankUDA$sensortype <- ""
pHdtankUDA$sensortype <- "UDA2182"
variable.names(pHdtankUDA)
# [1] "experiment"  "unit"        "unit_number" "date"        "pH"          "temp"        "sensortype"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
# 
# pHdtankUDA$date<- as.POSIXct(pHdtankUDA$date, tz = "UTC", "%m/%d/%Y")
pHdtankUDA$ObservationDate <- ""
pHdtankUDA$ObservationDate <- as.POSIXct(pHdtankUDA$date, tz = "UTC", "%m/%d/%y")
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


#breaking out the temperature information for the plot now that they are in the right format
TempdtankUDA <- pHdtankUDA
#|- - - - - - - - - - - - - 
variable.names(pHdtankUDA)



```


#### 6.2a) pH plots -Timeseries Plots - UDA sensor log filtered
```{r 6.2a) pH plots -Timeseries Plots - UDA sensor log filtered, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 6.2a) pH plots -Timeseries Plots - UDA sensor log filtered
#*********************************
variable.names(pHdtankUDA)
# [1] "experiment"      "unit"            "unit_number"     "date"            "pH"              "temp"           
# [7] "sensortype"      "ObservationDate"
pHdtankUDA <- subset( pHdtankUDA, select = -c(experiment,
                                         unit,
                                         date,
                                         temp))
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

pHdtankUDA$unit_number <- as.character(pHdtankUDA$unit_number)

pHdtankUDA$treatment <- ""
pHdtankUDA$treatment[pHdtankUDA$unit_number == "2" | pHdtankUDA$unit_number== "4" | pHdtankUDA$unit_number== "6"] <- "highCO2"
pHdtankUDA$treatment[pHdtankUDA$unit_number == "1" | pHdtankUDA$unit_number== "3" | pHdtankUDA$unit_number== "5"] <- "ambient"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# pHdtankUDA is the UDA pH logs
variable.names(pHdtankUDA)
pHdtankUDA$pH <- as.numeric(pHdtankUDA$pH)




# dRESPmsrGOODtreatments <- dRESPmsr %>% filter(Treatment %in% c("CUR", "CHG", "TMP", "n/a"))


# 
# Cdml %>% filter(deltaTempLag1 >1)
# pHdtankUDA.filtered <- pHdtankUDA %>% filter(pH )
# filteredFrame = filter(Cdml (aTemperature>= 5 & aTemperature<=30) )
# 
# subset(pHdtankUDA.filtered$pH >= 5 & pH<=10) 
# 
# pHdtankUDA.filtered <- as.character(pHdtankUDA.filtered$unit_number)



# pHdtankUDA.filtered <- pHdtankUDA %>% filter(pH >5)
# pHdtankUDA.filtered <- pHdtankUDA %>% filter(pH <10)


pHdtankUDA.filtered <- filter(pHdtankUDA,(pH>= 5 & pH<=10))


ggplot(pHdtankUDA.filtered, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=treatment, point=)) + 
  ggtitle("UDA tank data per tank") 


```


#### 6.3a) UDA tank data per tank (Tank 5 Early Problem Start Relay Problems) (Filtered 5-10 pH)
Tank 5 has early problem start problems (Data from Honeywell UDA sensor & display)
```{r 6.3a) UDA tank data per tank (Tank 5 Early Problem Start Relay Problems), echo=FALSE, message=FALSE, warning=FALSE}
# 
pHdtankUDA.filtered$unit_number <- as.character(pHdtankUDA.filtered$unit_number)

ggplot(pHdtankUDA.filtered, aes(x=ObservationDate, y=pH)) +
  geom_point(aes(colour=unit_number, point=)) +
  ggtitle("UDA tank data per tank (Tank 5 Early Problem Start Relay Problems)")
```



#### 6.3b) UDA tank data per tank (Filtered to show 6-8 pH)
```{r 6.3b) UDA tank data per tank (Filtered to show 6-8 pH), echo=FALSE, message=FALSE, warning=FALSE}
pHdtankUDA.filtered8.6 <- filter(pHdtankUDA,(pH>= 6 & pH<=8))

pHdtankUDA.filtered8.6$unit_number <- as.character(pHdtankUDA.filtered8.6$unit_number)

ggplot(pHdtankUDA.filtered8.6, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=unit_number, point=)) + 
  ggtitle("UDA tank data filtered (pH displayed between 6-8)") 

```
Appears that all Probes got "tired" after April
Tank 01's probe experienced exceptional drift 



#### 6.3c) UDA tank data per tank highlighted by Treatment (Filtered to show 6-8 pH)
```{r 6.3c) UDA tank data per tank highlighted by Treatment (Filtered to show 6-8 pH), echo=FALSE, message=FALSE, warning=FALSE}

pHdtankUDA.filtered8.6 <- filter(pHdtankUDA,(pH>= 6 & pH<=8))

pHdtankUDA.filtered8.6$unit_number <- as.character(pHdtankUDA.filtered8.6$unit_number)

ggplot(pHdtankUDA.filtered8.6, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=unit_number, point=)) + 
  ggtitle("UDA tank data filtered (Tank 5 Early Problem Start Relay Problems)") 
```




#### 6.4a) pH plots -Timeseries Plots - SPEC data 
```{r 6.4a) pH plots -Timeseries Plots - SPEC data, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 6.2a) pH plots -Timeseries Plots - SPEC data 
#*********************************
variable.names(dtank)

#  [1] "experiment"      "unit"            "unit_number"     "id_1"            "id_2"            "id_3"     
#  [7] "time"            "date"            "salinity"        "pHat25"          "fileName"        "unit_ID"        
# [13] "alk"             "insituTemp"      "pHinsitu"        "dateString"      "ObservationDate" "treatment"  

pHdtank <- subset( dtank, select = -c(experiment,
                                         unit,
                                         id_1,
                                         id_2,
                                         id_3,
                                         time,
                                         date,
                                         salinity,
                                         pHat25,
                                         fileName,
                                         unit_ID,
                                         alk,
                                         insituTemp,
                                         dateString))

variable.names(pHdtank)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

colnames(pHdtank)[2]<-c("pH")

# SPECpHtempfile <- pHdtank$pHat25
# pHdtank$pH <- ""
# pHdtank$pH <- SPECpHtempfile 
# pHdtank <- subset( dtank, select = -c(pHat25))
variable.names(pHdtank)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# pHdtank$treatment <- ""
# pHdtank$treatment[pHdtank$unit_number == "2" | pHdtank$unit_number== "4" | pHdtank$unit_number== "6"] <- "highCO2"
# pHdtank$treatment[pHdtank$unit_number == "1" | pHdtank$unit_number== "3" | pHdtank$unit_number== "5"] <- "ambient"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# pHdtank$ObservationDate <- ""
# pHdtank$ObservationDate<- as.POSIXct(pHdtank$date, tz = "UTC", "%m/%d/%Y")

## Ocean Optics USB 230 2000+ Fiber Optic Spectrometer, Ocean View Spectroscopy software and 5mM solution of Sigma Aldritch m-cresol purple indicator dye

pHdtank$sensortype <- ""
pHdtank$sensortype <- "OceanOptics"

#pHdtank is the SPEC record logs 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


pHtanklog <- merge(pHdtank, pHdtankUDA, all = TRUE)
dim(pHtanklog)
variable.names(pHtanklog)


#why did these other values APPEAR?!!!!
# pHtanklog <- subset( pHtanklog, select = -c(experiment,
#                                          unit,
#                                          date,
#                                          temp))
# variable.names(pHtanklog)
# ggplot(pHtanklog, aes(x=ObservationDate, y=pH)) + 
#   geom_point(aes(colour=sensortype, point=))

```




#### 6.4b) Water Chemistry Plots between different probe types
```{r 6.4b) Different Salinity Probes Data}
pHplot1 <- ggplot(pHtanklog, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=sensortype, point=)) + 
  ylim(5,10) +
  ggtitle("pH Values from UDA probes and Orion insitu SPEC measurements") 
pHplot1

```


#### 6.5c Water Chemistry Plots between different treatment timeseries
```{r 6.5c Different Salinity Probes Data}
pHplot2 <- ggplot(pHtanklog, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=treatment, point=)) + 
  ylim(6.5,8.5) +
  ggtitle("pH Values from UDA probes and Orion insitu SPEC measurements") 
pHplot2

```

# Executive Summary


UDA sensors for ambient tank 01 appears to experience significant drift April and beyond.
Chase's UDA data could confirm if pH drift was actual, was a real world seasonal effect
SPEC data confirms the High CO2 treatment target pH. 

```{r}
pHplot1
```


```{r}
pHplot2
```


```{r}
PSUplot
```


```{r}
pHtanklog.summary <- pHtanklog %>% group_by(treatment, sensortype) %>%
  dplyr::summarize(sd = sd(pH, na.rm = TRUE), 
            mean = mean(pH, na.rm = TRUE), 
            median = median(pH, na.rm = TRUE),
            IQR = IQR(pH, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)

write.csv(pHtanklog.summary, "2021.02.02_pHtanklog.summary.csv")
kable(pHtanklog.summary, digits = 4)


```





```{r}
pHboxplots1 <- ggplot(pHtanklog, aes(treatment, pH)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = pHtanklog.summary, aes(x=treatment, y=mean), size=5, color = "purple") + 
            geom_errorbar(data = pHtanklog.summary, 
                          aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = pHtanklog.summary,
                          aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~TrialID) +
            ggtitle("Salmon Shed pH grouped by Treatment") +
            theme_bw() 

pHboxplots1

```

```{r}
pHboxplots2 <- ggplot(pHtanklog, aes(sensortype, pH)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = pHtanklog.summary, aes(x=treatment, y=mean), size=5, color = "purple") +
            geom_errorbar(data = pHtanklog.summary, 
                          aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = pHtanklog.summary,
                          aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~TrialID) +
            ggtitle("Salmon Shed pH grouped by Sensor") +
            theme_bw() 

pHboxplots2
```



```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT

