
---
title: "Characterizing Salmon Shed Tank Temperature, Conductivity, and Water Chemistry"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Salmon Shed Tanks
Date: 2018-2019 (R document January 2021)


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
library(arsenal)
library(compareDF)
#for graphing
library(ggplot2)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```



### 1.) Setting Working Directory
```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks")
```


### 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 2.) Creating the initial Dataframe, dtank
#*********************************


dtank <- read.csv(file = "2021.01.05_shinyappSPECdatawithoutTreatmentFile.csv", stringsAsFactors = FALSE)
dim(dtank)


```
Dataframes mentioned throughout the document
dtank = SPEC sourced data 
dtankUDA= UDA sourced 

SPECCNDCT conductivity measurements recording for SEPC
UDACNDCT conductivity measurements recording from Honeywell UDA probe



### 3.) Creating dateTime objects 
```{r 3.) Creating dateTime objects, echo=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 3.) Creating dateTime objects  
#*********************************

dtank$ObservationDate <- as.Date(dtank$date)
dtank$ObservationDate<- as.POSIXct(dtank$date, tz = "UTC", "%m/%d/%y")


```
First Observation recorded as of August 10th 2018


### 4.) Creating Treatments
```{r 4.) Creating Treatments, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 4.) Creating Treatments 
#********************************
# 6 tanks
# 3 replicates of the high CO2 conditions
# 3 replicates of ambient conditions

dtank$unit_number <- as.character(dtank$unit_number)
dtank$treatment <- ""
dtank$treatment[dtank$unit_number == "2" | dtank$unit_number== "4" | dtank$unit_number== "6"] <- "highCO2"
dtank$treatment[dtank$unit_number == "1" | dtank$unit_number== "3" | dtank$unit_number== "5"] <- "ambient"


```


### 5.) Timeseries Plots
#### 5.1) Salinity Plots
```{r 5.1) Salinity Plots, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.1) Timeseries Plot
#*********************************
# dtank$salinity <- as.numeric(dtank$salinity)

ggplot(dtank, aes(x=ObservationDate, y=salinity)) + 
  geom_point(aes(colour=, point=)) + 
  ggtitle("Salinity Values from Handheld Orion Salinity Probe") 



```



#### 5.1a) Merging salinity data for plots
```{r 5.1a) Merging salinity data for plots, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.1a) Salinity Data for Timeseries Plot
#*********************************

UDAconductivity <- read.csv(file = "2018 SS UDA Log.csv", stringsAsFactors = FALSE)
dim(UDAconductivity)

UDAconductivity$ObservationDate <- ""
# UDAconductivity$Date <- as.numeric(UDAconductivity$Date)
# UDAconductivity$ObservationDate <- as.Date(UDAconductivity$Date)
UDAconductivity$ObservationDate<- as.POSIXct(UDAconductivity$Date, tz = "UTC", "%m/%d/%Y")
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

variable.names(UDAconductivity)
UDACNDCT <- subset( UDAconductivity, select = -c(Date,
                                         T4.pH,
                                         T4.temp,         
                                         T3.pH,
                                         T3.temp,
                                         T5.pH,
                                         T5.temp,
                                         T6.pH,
                                         T6.temp,
                                         T2.pH,           
                                         T2.temp,         
                                         T1.pH,          
                                         T1.temp))
colnames(UDACNDCT)[1] <- "salinity"
UDACNDCT$sensortype <- ""
# Toroidal Conductivity Monitor Model Q46CT
UDACNDCT$sensortype <- "HoneywellUDA"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

SPECCNDCT <- subset( dtank, select = -c(unit,
                                         unit_number,
                                         pHinsitu,
                                         dateString,
                                         experiment, 
                                         id_1, 
                                         id_2, 
                                         id_3, 
                                         time, 
                                         date, 
                                         pHat25, 
                                         fileName, 
                                         unit_ID, 
                                         alk, 
                                         treatment,
                                         insituTemp))
SPECCNDCT$sensortype <- ""
# ThermoScientific Orion Star A322
SPECCNDCT$sensortype <- "Orion"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dTankCNDCT <- merge(UDACNDCT, SPECCNDCT, all = TRUE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```
Determine if salinity units are both PSU



#### 5.1b) Different Salinity Probes' Data
```{r 5.1b) Different Salinity Probes Data, echo=FALSE, message=FALSE, warning=FALSE}

PSUplot <- ggplot(dTankCNDCT, aes(x=ObservationDate, y=salinity)) + 
  geom_point(aes(colour=sensortype, point=)) + 
  ggtitle("Salmon Shed Salinity Values") 
PSUplot

```


#### 5.2) pH plots per tank timeseries
```{r 5.2) pH plots per tank timeseries, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 5.2) pH plots -Timeseries Plots - Bringing Together UDA plots for the different tanks
#*********************************

UDAtank01 <- read.csv(file = "Tank01UDALog.csv", stringsAsFactors = FALSE)
UDAtank02 <- read.csv(file = "Tank02UDALog.csv", stringsAsFactors = FALSE)
UDAtank04 <- read.csv(file = "Tank04UDALog.csv", stringsAsFactors = FALSE)
UDAtank05 <- read.csv(file = "Tank05UDALog.csv", stringsAsFactors = FALSE)
UDAtank06 <- read.csv(file = "Tank06UDALog.csv", stringsAsFactors = FALSE)

pHdtankUDA <- rbind(UDAtank06,
                    UDAtank05,  
                    UDAtank04,
                    UDAtank02,
                    UDAtank01)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


```



#### 5.2a) pH plots -Timeseries Plots - UDA
```{r 5.2a) pH plots -Timeseries Plots - UDA, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.2a) pH plots -Timeseries Plots - UDA sensor type, update dates
#*********************************

variable.names(pHdtankUDA)
# > variable.names(pHdtankUDA)
# [1] "experiment"  "unit"        "unit_number" "date"        "pH"          "temp" 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


# not sure if this is the correct UDA sensor model number 
# UDA2182UniversalDualAnalyzer
pHdtankUDA$sensortype <- ""
pHdtankUDA$sensortype <- "UDA2182"
variable.names(pHdtankUDA)
# [1] "experiment"  "unit"        "unit_number" "date"        "pH"          "temp"        "sensortype"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
# 
# pHdtankUDA$date<- as.POSIXct(pHdtankUDA$date, tz = "UTC", "%m/%d/%Y")
pHdtankUDA$ObservationDate <- ""
pHdtankUDA$ObservationDate <- as.POSIXct(pHdtankUDA$date, tz = "UTC", "%m/%d/%y")
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


#breaking out the temperature information for the plot now that they are in the right format
TempdtankUDA <- pHdtankUDA
#|- - - - - - - - - - - - - 
variable.names(pHdtankUDA)



```


#### 5.2a) pH plots -Timeseries Plots - UDA sensor log filtered
```{r 5.2a) pH plots -Timeseries Plots - UDA sensor log filtered, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.2a) pH plots -Timeseries Plots - UDA sensor log filtered
#*********************************
variable.names(pHdtankUDA)
# [1] "experiment"      "unit"            "unit_number"     "date"            "pH"              "temp"           
# [7] "sensortype"      "ObservationDate"
pHdtankUDA <- subset( pHdtankUDA, select = -c(experiment,
                                         unit,
                                         date,
                                         temp))
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

pHdtankUDA$unit_number <- as.character(pHdtankUDA$unit_number)

pHdtankUDA$treatment <- ""
pHdtankUDA$treatment[pHdtankUDA$unit_number == "2" | pHdtankUDA$unit_number== "4" | pHdtankUDA$unit_number== "6"] <- "highCO2"
pHdtankUDA$treatment[pHdtankUDA$unit_number == "1" | pHdtankUDA$unit_number== "3" | pHdtankUDA$unit_number== "5"] <- "ambient"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# pHdtankUDA is the UDA pH logs
variable.names(pHdtankUDA)
pHdtankUDA$pH <- as.numeric(pHdtankUDA$pH)




# dRESPmsrGOODtreatments <- dRESPmsr %>% filter(Treatment %in% c("CUR", "CHG", "TMP", "n/a"))


# 
# Cdml %>% filter(deltaTempLag1 >1)
# pHdtankUDA.filtered <- pHdtankUDA %>% filter(pH )
# filteredFrame = filter(Cdml (aTemperature>= 5 & aTemperature<=30) )
# 
# subset(pHdtankUDA.filtered$pH >= 5 & pH<=10) 
# 
# pHdtankUDA.filtered <- as.character(pHdtankUDA.filtered$unit_number)



# pHdtankUDA.filtered <- pHdtankUDA %>% filter(pH >5)
# pHdtankUDA.filtered <- pHdtankUDA %>% filter(pH <10)


pHdtankUDA.filtered <- filter(pHdtankUDA,(pH>= 5 & pH<=10))


ggplot(pHdtankUDA.filtered, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=treatment, point=)) + 
  ggtitle("UDA tank data per tank") 


```


#### 5.3a) UDA tank data per tank (Tank 5 Early Problem Start Relay Problems) (Filtered 5-10 pH)
Tank 5 has early problem start problems (Data from Honeywell UDA sensor & display)
```{r 5.3a) UDA tank data per tank (Tank 5 Early Problem Start Relay Problems), echo=FALSE, message=FALSE, warning=FALSE}
# 
pHdtankUDA.filtered$unit_number <- as.character(pHdtankUDA.filtered$unit_number)

ggplot(pHdtankUDA.filtered, aes(x=ObservationDate, y=pH)) +
  geom_point(aes(colour=unit_number, point=)) +
  ggtitle("UDA tank data per tank (Tank 5 Early Problem Start Relay Problems)")
```



#### 5.3b) UDA tank data per tank (Filtered to show 6-8 pH)
```{r 5.3b) UDA tank data per tank (Filtered to show 6-8 pH), echo=FALSE, message=FALSE, warning=FALSE}
pHdtankUDA.filtered8.6 <- filter(pHdtankUDA,(pH>= 6 & pH<=8))

pHdtankUDA.filtered8.6$unit_number <- as.character(pHdtankUDA.filtered8.6$unit_number)

ggplot(pHdtankUDA.filtered8.6, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=unit_number, point=)) + 
  ggtitle("UDA tank data filtered (pH displayed between 6-8)") 

```
Appears that all Probes got "tired" after April
Tank 01's probe experienced exceptional drift 



#### 5.3c) UDA tank data per tank highlighted by Treatment (Filtered to show 6-8 pH)
```{r 5.3c) UDA tank data per tank highlighted by Treatment (Filtered to show 6-8 pH), echo=FALSE, message=FALSE, warning=FALSE}

pHdtankUDA.filtered8.6 <- filter(pHdtankUDA,(pH>= 6 & pH<=8))

pHdtankUDA.filtered8.6$unit_number <- as.character(pHdtankUDA.filtered8.6$unit_number)

ggplot(pHdtankUDA.filtered8.6, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=unit_number, point=)) + 
  ggtitle("UDA tank data filtered (Tank 5 Early Problem Start Relay Problems)") 
```




#### 5.4a) pH plots -Timeseries Plots - SPEC data 
```{r 5.4a) pH plots -Timeseries Plots - SPEC data, echo=FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.2a) pH plots -Timeseries Plots - SPEC data 
#*********************************
variable.names(dtank)

#  [1] "experiment"      "unit"            "unit_number"     "id_1"            "id_2"            "id_3"     
#  [7] "time"            "date"            "salinity"        "pHat25"          "fileName"        "unit_ID"        
# [13] "alk"             "insituTemp"      "pHinsitu"        "dateString"      "ObservationDate" "treatment"  

pHdtank <- subset( dtank, select = -c(experiment,
                                         unit,
                                         id_1,
                                         id_2,
                                         id_3,
                                         time,
                                         date,
                                         salinity,
                                         fileName,
                                         unit_ID,
                                         alk,
                                         insituTemp,
                                         pHinsitu,
                                         dateString))

variable.names(pHdtank)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

colnames(pHdtank)[2]<-c("pH")

# SPECpHtempfile <- pHdtank$pHat25
# pHdtank$pH <- ""
# pHdtank$pH <- SPECpHtempfile 
# pHdtank <- subset( dtank, select = -c(pHat25))
variable.names(pHdtank)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# pHdtank$treatment <- ""
# pHdtank$treatment[pHdtank$unit_number == "2" | pHdtank$unit_number== "4" | pHdtank$unit_number== "6"] <- "highCO2"
# pHdtank$treatment[pHdtank$unit_number == "1" | pHdtank$unit_number== "3" | pHdtank$unit_number== "5"] <- "ambient"
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# pHdtank$ObservationDate <- ""
# pHdtank$ObservationDate<- as.POSIXct(pHdtank$date, tz = "UTC", "%m/%d/%Y")

## Ocean Optics USB 230 2000+ Fiber Optic Spectrometer, Ocean View Spectroscopy software and 5mM solution of Sigma Aldritch m-cresol purple indicator dye

pHdtank$sensortype <- ""
pHdtank$sensortype <- "OceanOptics"

#pHdtank is the SPEC record logs 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


pHtanklog <- merge(pHdtank, pHdtankUDA, all = TRUE)
dim(pHtanklog)
variable.names(pHtanklog)


#why did these other values APPEAR?!!!!
# pHtanklog <- subset( pHtanklog, select = -c(experiment,
#                                          unit,
#                                          date,
#                                          temp))
# variable.names(pHtanklog)
# ggplot(pHtanklog, aes(x=ObservationDate, y=pH)) + 
#   geom_point(aes(colour=sensortype, point=))

```




#### 5.4b Water Chemistry Plots between different probe types
```{r 5.4b) Different Salinity Probes Data}
pHplot1 <- ggplot(pHtanklog, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=sensortype, point=)) + 
  ylim(5,10) +
  ggtitle("pH Values from UDA probes and Orion insitu SPEC measurements") 
pHplot1

```


#### 5.5c Water Chemistry Plots between different treatment timeseries
```{r 5.5c Different Salinity Probes Data}
pHplot2 <- ggplot(pHtanklog, aes(x=ObservationDate, y=pH)) + 
  geom_point(aes(colour=treatment, point=)) + 
  ylim(6.5,8.5) +
  ggtitle("pH Values from UDA probes and Orion insitu SPEC measurements") 
pHplot2

```

# Executive Summary


UDA sensors for ambient tank 01 appears to experience significant drift April and beyond.
Chase's UDA data could confirm if pH drift was actual, was a real world seasonal effect
SPEC data confirms the High CO2 treatment target pH. 

```{r}
pHplot1
```


```{r}
pHplot2
```


```{r}
PSUplot
```


```{r}
pHtanklog.summary <- pHtanklog %>% group_by(treatment, sensortype) %>%
  dplyr::summarize(sd = sd(pH, na.rm = TRUE), 
            mean = mean(pH, na.rm = TRUE), 
            median = median(pH, na.rm = TRUE),
            IQR = IQR(pH, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
```





```{r}
pHboxplots1 <- ggplot(pHtanklog, aes(treatment, pH)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = pHtanklog.summary, aes(x=treatment, y=mean), size=5, color = "purple") + 
            geom_errorbar(data = pHtanklog.summary, 
                          aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = pHtanklog.summary,
                          aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~TrialID) +
            ggtitle("Standard dSlopes Values grouped by Treatment and Corrected Slope") +
            theme_bw() 

pHboxplots1

```




```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT

