
---
title: "Characterizing Salmon Shed Tank Temperature, Conductivity, and Water Chemistry"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Salmon Shed Tanks
Date: 2018-2019 (R document January-April 2021)

CRB_JUVambientsalmonshedconditions(2018-2019)TempMasterFile(2021.03.31)


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(here)
library(stringr)
library(data.table)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
library(arsenal)
library(compareDF)
library(metacsv)
#for graphing
library(ggplot2)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```



# 1.) Setting Working Directory
```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
# setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks/01_rawData")


```


# 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 2.) Creating the initial Dataframes
#*********************************


#set working directory to the correct folder
temp_Log <- read_csv(here::here("02_processedData",
                          "MasterTimeSeries","2021.03.31_Master_Temperature_log.csv"))

temp_pH <- read_csv(here::here("02_processedData",
                               "MasterTimeSeries","2021.03.31_pH_timeseries_log.csv"))

temp_salinty <- read_csv(here::here("02_processedData",
                                    "MasterTimeSeries","2021.03.31_salinity_timeseries_log.csv"))

```


#3.) Master Dataframe Salinity, pH & Temp
```{r Master Dataframe Salinity, pH & Temp}
#*********************************
## 3.) Creating a Master Dataframe - Salinity, pH, & temp
#********************************

inputs_timeseries <- merge(merge(
  temp_Log,
  temp_pH, all = TRUE),
  temp_salinty, all = TRUE)


## First Juvenile Observation in Salmon Shed "2018-08-19 23:59:00"
  # On August 8/20th
## Last Juvenile Observation in Salmon Shed "2019-07-10 23:59:00" 

inputs_timeseries$ObservationDate <- as.POSIXct(inputs_timeseries$ObservationDate, tz = "UTC", "%m/%d/%y")


inputs_timeseries <- filter(inputs_timeseries,
   ObservationDate >= as.POSIXct("2018-08-19 23:59:00", tz = "UTC") & ObservationDate < as.POSIXct("2019-07-10 23:59:00", tz = "UTC"))

inputs_timeseries <- inputs_timeseries[order(inputs_timeseries$ObservationDate),]
inputs_timeseries[order(inputs_timeseries$ObservationDate),]

head(inputs_timeseries$ObservationDate)
# [1] "2018-08-23 UTC"
tail(inputs_timeseries$ObservationDate)
# [1] "2019-07-10 UTC" 

# we have a three day delay in monitoring

```



# 3.1) Master Dataframe Temperature Check (Plot)
```{r Master Temperature Check Plot}

ggplot(inputs_timeseries, aes(ObservationDate, temp)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "blue") +
            # facet_wrap(~TrialID) +
            ggtitle("Temperature Timeseries (MasterFile)") +
            theme_bw()

```




# 3.2) Master Dataframe Temperature Check (Plot)
```{r Master Temperature Check Plot}

ggplot(inputs_timeseries, aes(ObservationDate, pH)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "blue") +
            # facet_wrap(~TrialID) +
            ggtitle("pH Timeseries (MasterFile)") +
            theme_bw()

```





# 3.3) Master Dataframe Temperature Check (Plot)
```{r Master Temperature Check Plot}

ggplot(inputs_timeseries, aes(ObservationDate, salinity)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "blue") +
            # facet_wrap(~TrialID) +
            ggtitle("Salinity Timeseries (MasterFile)") +
            theme_bw()

```



# 3.4) Master Dataframe input filters
```{r 3.4) Master Dataframe input filters}

# filtering unreasonable observations
inputs_timeseries <- filter(inputs_timeseries, (temp >= 5 & temp <= 30) | (pH >= 6 & pH <= 9) | (salinity >= 2 & salinity <= 55))

```


# 3.5) Master Dataframe Temperature Check (Plot)
```{r Master Temperature Check Plot}

ggplot(inputs_timeseries, aes(ObservationDate, temp)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "blue") +
            # facet_wrap(~TrialID) +
            ggtitle("Temperature Timeseries (MasterFile)") +
            theme_bw()

```







#4.) Observation Month
```{r Observation Month}

#*********************************
## 4.) Observation Month
#********************************

inputs_timeseries$ObservationMonth <- ""
inputs_timeseries <- inputs_timeseries %>% group_by(ObservationDate)
inputs_timeseries <- inputs_timeseries[order(inputs_timeseries$ObservationDate),]
head(inputs_timeseries$ObservationDate)

tail(inputs_timeseries$ObservationDate)

inputs_timeseries$ObservationMonth <- format(inputs_timeseries$ObservationDate, "%Y-%m-%B")

# 
# salinity_timeseries <- temp_salinty
# salinity_timeseries$ObservationMonth <- format(salinity_timeseries$ObservationDate, "%Y-%m-%B")

```



#5.) Summary Month Tables
```{r Summary Months}
#*********************************
## 4.) Observation Month
#********************************

# Creating the Mega-Month Table
# pivot_wider()

# Creating a string of variables from the summary function output
# # mean (sd) paste(mean, " (", sd, ")", sep = "")
# round(mean, 2)

# pivot_wider(names_from = sensortype, values_from = mean)
# pivot_wider(names_from = sensortype, values_from = c(mean, sd))



SalmonShed_temp_summary <- inputs_timeseries %>% group_by(ObservationMonth ,sensortype) %>%
  dplyr::summarize(sd = sd(temp, na.rm = TRUE), 
            mean = mean(temp, na.rm = TRUE), 
            # median = median(temp, na.rm = TRUE),
            # IQR = IQR(temp, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
SalmonShed_temp_summary

SalmonShed_temp_summary <- na.omit(SalmonShed_temp_summary)
kable(SalmonShed_temp_summary, digits = 4)
write.csv(SalmonShed_temp_summary, "CRB_JUV_SalmonShed_sensortype_temp_summary_2021.03.31.csv")



SalmonShed_pH_summary <- inputs_timeseries %>% group_by(ObservationMonth, treatment, sensortype) %>%
  dplyr::summarize(sd = sd(pH, na.rm = TRUE), 
            mean = mean(pH, na.rm = TRUE), 
            # median = median(pH, na.rm = TRUE),
            # IQR = IQR(pH, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
SalmonShed_pH_summary

SalmonShed_pH_summary <- na.omit(SalmonShed_pH_summary)
kable(SalmonShed_pH_summary, digits = 4)
write.csv(SalmonShed_pH_summary, "CRB_JUV_SalmonShed_sensortype_pH_summary_2021.03.31.csv")




SalmonShed_salinity_summary <- inputs_timeseries %>% group_by(ObservationMonth, sensortype) %>%
  dplyr::summarize(sd = sd(salinity, na.rm = TRUE), 
            mean = mean(salinity, na.rm = TRUE), 
            # median = median(salinity, na.rm = TRUE),
            # IQR = IQR(salinity, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
SalmonShed_salinity_summary

SalmonShed_salinity_summary <- na.omit(SalmonShed_salinity_summary)
kable(SalmonShed_salinity_summary, digits = 4)
write.csv(SalmonShed_salinity_summary, "CRB_JUV_SalmonShed_sensortype_salinity_summary_2021.03.31.csv")



# SalmonShed_Salinity_summary <- salinity_timeseries %>% group_by(ObservationMonth, sensortype) %>% 
#   dplyr::summarize(sd = sd(salinity, na.rm = TRUE), 
#             mean = mean(salinity, na.rm = TRUE), 
#             median = median(salinity, na.rm = TRUE),
#             IQR = IQR(salinity, na.rm = TRUE),
#             n = n()) %>%
#   mutate(se = sd/sqrt(n)) %>%
#   mutate(ci = se*1.96)
# SalmonShed_Salinity_summary
# 
# kable(SalmonShed_Salinity_summary, digits = 4)
# 
# write.csv(SalmonShed_Salinity_summary, "CRB_JUV_SalmonShed_sensortype_salinity_summary_2021.03.23.csv")


```


### 5.a) Salmon Shed Temp Summary Table Clean Up
```{r}
# SalmonShed_temp_summary

SalmonShed_temp_summary <- na.omit(SalmonShed_temp_summary)
kable(SalmonShed_temp_summary, digits = 4)


wider_temp <- SalmonShed_temp_summary %>% select(ObservationMonth, sensortype, mean, sd, se) %>% pivot_wider(names_from = c(sensortype), values_from = c(mean, sd, se), names_glue = "{sensortype}: {.value}")

write.csv(wider_temp, "CRB_JUV_SalmonShed_temp_summaryWIDE_2021.03.31.csv")


```




### 5.b) Salmon Shed pH Summary Table Clean Up
```{r}
# SalmonShed_pH_summary

SalmonShed_pH_summary <- na.omit(SalmonShed_pH_summary)
kable(SalmonShed_pH_summary, digits = 4)


pretty_wider_pH <- SalmonShed_pH_summary %>% select(ObservationMonth, treatment, sensortype, mean, sd, se) %>% pivot_wider(names_from = c(sensortype), values_from = c(mean, sd, se)) %>%
  mutate(pretty = paste(round(mean_OceanOptics1.6.7,2), " (", round(se_OceanOptics1.6.7,2),")")) %>% mutate(pretty = paste(round(mean_OceanOptics1.6.7,2), " (", round(mean_OceanOptics1.6.7-1.96 *se_OceanOptics1.6.7, 2), "-", round(mean_OceanOptics1.6.7+1.96 *se_OceanOptics1.6.7, 2), ")"))

kable(pretty_wider_pH, digits = 4)
         

wider_pH <- SalmonShed_pH_summary %>% select(ObservationMonth, treatment, sensortype, mean, sd, se) %>% pivot_wider(names_from = c(sensortype), values_from = c(mean, sd, se)) %>%
  mutate(pretty = paste(round(mean_OceanOptics1.6.7,2), " (", round(se_OceanOptics1.6.7,2),")"))

kable(wider_pH, digits = 4)



#          
# mutate(pretty = paste(round(mean,2), "(round(se,2), ")")")
# mutate(pretty = paste(round(mean,2), " (", round(se,2), ")")




write.csv(wider_pH, "CRB_JUV_SalmonShed_pH_summaryWIDE_2021.03.31.csv")


```





### 5.c) Salmon Shed Salinity Summary Table Clean Up
```{r}
# SalmonShed_salinity_summary

SalmonShed_pH_summary <- na.omit(SalmonShed_pH_summary)
kable(SalmonShed_pH_summary, digits = 4)


wider_salinity <- SalmonShed_salinity_summary %>% select(ObservationMonth, sensortype, mean, sd, se) %>% pivot_wider(names_from = c(sensortype), values_from = c(mean, sd, se), names_glue = "{sensortype}: {.value}")

kable(wider_salinity , digits = 4)

write.csv(wider_salinity , "CRB_JUV_SalmonShed_salinity_summaryWIDE_2021.03.31.csv")


```






# 6.) Summary Month & Plots

```{r 6.) Summary Month & Plots}

#*********************************
## 6.) Summary Month & Plots - Temperature
#*********************************

sumMonth_boxplot <- ggplot(inputs_timeseries, aes(ObservationMonth, temp)) +
            # geom_jitter(color = "grey") +
            geom_jitter(data = inputs_timeseries, aes(ObservationMonth, temp)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = SalmonShed_temp_summary, aes(x=sensortype, y=mean), size=5, color = "purple") +
            geom_errorbar(data = SalmonShed_temp_summary,
                          aes(x=sensortype, y=mean, ymin = mean-sd, ymax = mean+sd),
                          color = "blue") +
            geom_errorbar(data = SalmonShed_temp_summary,
                          aes(x=sensortype, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~droplevels(filter(inputs_timeseries, 
            #                               senosortype != "OceanOptics1.6.7"))) +
            xlab("ObservationMonth") +
            ylab("Temperature") +
            ggtitle("Temperatures Per Month") +
            theme_bw() 

sumMonth_boxplot



```



```{r}

#*********************************
## 7.) Summary Month & Plots - Salinity
#*********************************

sumMonth_boxplot <- ggplot(inputs_timeseries, aes(ObservationMonth, sensortype)) +
            # geom_jitter(color = "grey") +
            geom_jitter(data = inputs_timeseries, aes(ObservationMonth, sensortype)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            # geom_point(data = SalmonShed_temp_summary, aes(x=temp, y=mean), size=5, color = "purple") + 
            # geom_errorbar(data = SalmonShed_temp_summary, 
            #               aes(x=temp, y=mean, ymin = mean-sd, ymax = mean+sd), 
            #               color = "blue") +
            # geom_errorbar(data = SalmonShed_temp_summary,
            #               aes(x=temp, y=mean, ymin = mean-ci, ymax = mean+ci),
            #               colour = "red") +
            # # facet_wrap(~sensortype) +
            # xlab("ObservationMonth") +
            # ylab("Temperature") +
            ggtitle("Temperatures Per Month") +
            theme_bw() 

sumMonth_boxplot





```



```{r}
#*********************************
## 7.) Summary Month & Plots - pH
#*********************************

sumMonth_boxplot <- ggplot(inputs_timeseries, aes(ObservationMonth, sensortype)) +
            # geom_jitter(color = "grey") +
            geom_jitter(data = inputs_timeseries, aes(ObservationMonth, sensortype)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            # geom_point(data = SalmonShed_temp_summary, aes(x=temp, y=mean), size=5, color = "purple") + 
            # geom_errorbar(data = SalmonShed_temp_summary, 
            #               aes(x=temp, y=mean, ymin = mean-sd, ymax = mean+sd), 
            #               color = "blue") +
            # geom_errorbar(data = SalmonShed_temp_summary,
            #               aes(x=temp, y=mean, ymin = mean-ci, ymax = mean+ci),
            #               colour = "red") +
            # # facet_wrap(~sensortype) +
            # xlab("ObservationMonth") +
            # ylab("Temperature") +
            ggtitle("Temperatures Per Month") +
            theme_bw() 

sumMonth_boxplot
```







```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT

