
---
title: "Characterizing Salmon Shed Tank Temperature, Conductivity, and Water Chemistry"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Salmon Shed Tanks
Date: 2018-2019 (R document January-March 2021)

CRB_JUVambientsalmonshedconditions(2018-2019)SalinityMasterFile
CRB_JUVambientsalmonshedconditions(2018-2019)pHMasterFile(2021.03.23)
CRB_JUVambientsalmonshedconditions(2018-2019)TemperatureMasterFile



# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(here)
library(stringr)
library(data.table)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
library(arsenal)
library(compareDF)
library(metacsv)
#for graphing
library(ggplot2)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```



# 1.) Setting Working Directory
```{r 1.) Setting Working Directory, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks/01_rawData")



```


# 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 2.) Creating the initial Dataframes
#*********************************


#set working directory to the correct folder
# setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_DGNjuvenile.tanks")
# here()
# former "dtank"
dOrion <- read_csv(here::here("01_rawData","SpecData_2021.02.11_masterfile_salmonshed_chumhouse.csv"))

#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*

write_meta_template(dOrion, here::here("01_rawData","masterfile_salmonshed_chumhouse(2021.03.10).csv"),
                            embedded = TRUE)

# meta_dOrion <- read_meta(here("01_rawData",
#                              "masterfile_salmonshed_chumhouse_withMeta.csv"))

#|- - - - - - - - - - - - - - - - - - - - - - - - - -  - - - - - - - - - - - - |

# former "dUDAsalmon" and/or dfSalinity
dFishCareUDA <- read_csv(here::here("01_rawData", "2021.02.18_FishCareLog_salinity.csv")) 
dim(dFishCareUDA)
dFishCareUDA$temp <- as.numeric(dFishCareUDA$temp)
dFishCareUDA$salinity <- as.numeric(dFishCareUDA$salinity)

#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*

write_meta_template(dFishCareUDA, here::here("01_rawData",                                  "FishCareLog_salinity(2021.03.10).csv"),
                            embedded = TRUE)


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# former UDAconductivity
# Raw file from UDA
# dShedUDA <- read.csv(file = "2019 SS UDA Log.csv", stringsAsFactors = FALSE)
# dim(dShedUDA)
# Transformed File
dShedUDA <- read_csv(here::here("01_rawData", "2021.02.18_pH_UDA.csv"))
dim(dShedUDA)
dShedUDA$pH <- as.numeric(dShedUDA$pH)
dShedUDA$temp <- as.numeric(dShedUDA$temp)

#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*
write_meta_template(dShedUDA, here::here("01_rawData",                                  "UDA_pH_log(2021.03.10).csv"),
                            embedded = TRUE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dHOBOppt <- read_csv(here::here("01_rawData","2021.02.18b_dHOBOlogCNDCT.csv"))
dim(dHOBOppt)
#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*
write_meta_template(dHOBOppt, here::here("01_rawData",                          "dHOBOlogCNDCT(2021.03.10).csv"),
                            embedded = TRUE)


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dShedSalinity <- read_csv(here::here("01_rawData", "2019 SS UDA Log.csv"))

#*-*-*-*-*-*-*
# Meta Data 
#*-*-*-*-*-*-*
write_meta_template(dShedSalinity, here::here("01_rawData",                                  "2019 SS UDA Log(2021.03.10).csv"),
                            embedded = TRUE)

```



Dataframes mentioned throughout the document
dOrion = all SPEC files 
dFishCareUDA = information from Chase's fish care log 
dShedUDA = UDA information from the Salmon Shed recorded by OA lab personnel  
dHOBOppt = Includes salinity readings from the conductivity logger




# 3.) Creating dateTime objects 
```{r 3.) Creating dateTime objects, echo=FALSE, message=FALSE, warning=FALSE }
#*********************************
## 3.) Creating dateTime objects  
#*********************************
dOrion$ObservationDate <- ""
dOrion$ObservationDate <- as.POSIXct(dOrion$date, tz = "UTC", "%m/%d/%y")

dFishCareUDA$ObservationDate <- ""
dFishCareUDA$ObservationDate <- as.POSIXct(dFishCareUDA$Date, tz = "UTC", "%m/%d/%y")

dShedUDA$ObservationDate <- ""
dShedUDA$ObservationDate <- as.POSIXct(dShedUDA$date, tz = "UTC", "%m/%d/%y")

dHOBOppt$ObservationDate <- ""
dHOBOppt$ObservationDate <- as.POSIXct(dHOBOppt$dateTime, tz = "UTC", "%m/%d/%y %H:%M")

dShedSalinity$ObservationDate <- ""
dShedSalinity$ObservationDate <- as.POSIXct(dShedSalinity$Date, tz = "UTC", "%m/%d/%y")

```
First Observation recorded as of August 10th 2018


# 4.) Creating Treatments
```{r 4.) Creating Treatments}
#*********************************
## 4.) Creating Treatments 
#********************************
# 6 tanks
# 3 replicates of the high CO2 conditions
# 3 replicates of ambient conditions

# Review of 4 important datasets
names(dOrion)
names(dFishCareUDA)
names(dShedUDA)
names(dHOBOppt)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dOrion$unit_number <- as.character(dOrion$unit_number)
dOrion$treatment <- ""
dOrion$treatment[dOrion$unit_number == "2" | dOrion$unit_number== "4" | dOrion$unit_number== "6"] <- "highCO2"
dOrion$treatment[dOrion$unit_number == "1" | dOrion$unit_number== "3" | dOrion$unit_number== "5"] <- "ambient"
dOrion$treatment[dOrion$unit_number == "7"] <- "ambient"
dOrion$treatment[dOrion$unit_number == "8"] <- "ambient_chumhouse"

dOrion$location <- ""
dOrion$location[dOrion$treatment == "highCO2" | dOrion$treatment == "ambient" | dOrion$treatment == "ambient"] <- "salmonShed"

dOrion$location[dOrion$unit_number == "8"] <- "ambient_chumhouse"

dOrion$sensortype <- ""
dOrion$sensortype <- "OrionStarA112"

min(dOrion_Salinity$ObservationDate)


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#Treatment is being created for the Salinity Timeseries 
## - however no water chemistry data was collected
# all values are treated as chumhouse or salmon shed ambient
dFishCareUDA$treatment[dFishCareUDA$location == "salmonShed" ] <- "ambient"
dFishCareUDA$treatment[dFishCareUDA$location == "chumHouse" ] <- "ambient_chumhouse"

dFishCareUDA$sensortype <- ""
dFishCareUDA$sensortype[dFishCareUDA$location == "salmonShed" ] <- "SENSOREXtorodial"
dFishCareUDA$sensortype[dFishCareUDA$location == "chumHouse" ] <- "OrionStarA112"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# dShedUDA file uses same unit_number identifers as SPEC file
dShedUDA$unit_number <- as.character(dShedUDA$unit_number)
dShedUDA$treatment <- ""
dShedUDA$treatment[dShedUDA$unit_number == "2" | dShedUDA$unit_number== "4" | dShedUDA$unit_number== "6"] <- "highCO2"
dShedUDA$treatment[dShedUDA$unit_number == "1" | dShedUDA$unit_number== "3" | dShedUDA$unit_number== "5"] <- "ambient"

dShedUDA$sensortype <- ""
dShedUDA$sensortype <- "wallUDA_salmonShed"

dShedUDA$location <- ""
dShedUDA$location <- "salmonShed"

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dHOBOppt$treatment <- ""
dHOBOppt$treatment <- "ambient"


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dShedSalinity$treatment<- ""
dShedSalinity$treatment<- "ambient"
dShedSalinity$location <- ""
dShedSalinity$location <- "salmonShed"
dShedSalinity$sensortype <- ""
dShedSalinity$sensortype <- "SENSOREXtorodial"

```




# 4.1) Water Chemistry - Cleaning and Transposing UDA Data
#### 4.1) pH plots per tank timeseries
```{r 4.1) pH plots per tank timeseries, echo=FALSE, message=FALSE, warning=FALSE}

#*********************************
## 4.1) pH plots -Timeseries Plots - Bringing Together UDA plots for the different tanks
#*********************************


UDAtank01 <- read_csv(here::here("02_processedData", "Tank01UDALog.csv"))
UDAtank02 <- read_csv(here::here("02_processedData", "Tank02UDALog.csv"))
UDAtank04 <- read_csv(here::here("02_processedData", "Tank04UDALog.csv"))
UDAtank05 <- read_csv(here::here("02_processedData", "Tank05UDALog.csv"))
UDAtank06 <- read_csv(here::here("02_processedData", "Tank06UDALog.csv"))

pHdtankUDA <- rbind(UDAtank06,
                    UDAtank05,  
                    UDAtank04,
                    UDAtank02,
                    UDAtank01)

#|- -- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

pHdtankUDA$ObservationDate <- ""
pHdtankUDA$ObservationDate <- as.POSIXct(pHdtankUDA$date, tz = "UTC", "%m/%d/%y")
pHdtankUDA$pH <- as.numeric(pHdtankUDA$pH)
pHdtankUDA$temp <- as.numeric(pHdtankUDA$temp)

#|- -- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

pHdtankUDA$unit_number <- as.character(pHdtankUDA$unit_number)
pHdtankUDA$treatment <- ""
pHdtankUDA$treatment[pHdtankUDA$unit_number == "2" | pHdtankUDA$unit_number== "4" | pHdtankUDA$unit_number== "6"] <- "highCO2"
pHdtankUDA$treatment[pHdtankUDA$unit_number == "1" | pHdtankUDA$unit_number== "3" | pHdtankUDA$unit_number== "5"] <- "ambient"


pHdtankUDA$sensortype <- ""
pHdtankUDA$sensortype <- "UDA2182durfet"

pHdtankUDA$location <- ""
pHdtankUDA$location <- "salmonShed"


names(pHdtankUDA)

```



# 5.) Salinity and Waterchemistry Dataframes
```{r 5.0 Creating a Master Dataframe - Salinity, pH, & temp}

#*********************************
## 5.0) Creating a Master Dataframe - Salinity, pH, & temp
#********************************

# names(pHdtankUDA)
# "experiment" 
# "unit"            
# "unit_number"     
# "date"            
# "pH"             
# "temp"            
# "ObservationDate" 
# "treatment"  
# "sensortype"

dtankUDA_pH <- select(pHdtankUDA,
                      pH,
                      ObservationDate,
                      treatment,
                      location,
                      sensortype)

SPECinsitu_pH <- select(dOrion,
                          pH,
                          ObservationDate,
                          treatment,
                          location,
                          sensortype)

SPECinsitu_pH$sensortype <- "OceanOptics1.6.7"


pH_timeseries <- merge(
  SPECinsitu_pH,
  dtankUDA_pH, all = TRUE)

pH_timeseries <- na.omit(pH_timeseries)
write.csv(pH_timeseries, "2021.03.31_pH_timeseries_log.csv")


```





```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT

